README.md

### 2024-01-30 README.Rmd
title

# Microclimatic buffering prevents homogenization of relict alpine communities

@@

> Jiménez-Alfaro B, Fernández-Pascual E, Espinosa del Alba C, Marcenò C (2023) Microclimatic buffering prevents homogenization of relict alpine communities.

>>>>

# Spatiotemporal patterns of microclimatic buffering in relict alpine communities

@@

> Jiménez-Alfaro B, Fernández-Pascual E, Espinosa del Alba C, Marcenò C (2023) Spatiotemporal patterns of microclimatic buffering in relict alpine communities.
